Appendix

### 2021-08-25 draft.Rmd
Clean appendix

test_fig_mat_met <- plot_grid(
  map_st,
  plot_grid( plot_grid(tps_bm_dec, tps_bm_inc)), 
  plot_grid(plotlist = tps_dec_inc),
  nrow = 3
)
save_plot(test_fig_mat_met,
  file = get_mypath("figures", "matmet.png") 
)
```

>>>>

test_fig_mat_met <- plot_grid(
  map_st,
  plot_grid( plot_grid(tps_bm_dec, tps_bm_inc)),
  plot_grid(plotlist = tps_dec_inc),
  nrow = 3
)
save_plot(
  test_fig_mat_met,
  base_height = 7,
  base_asp = 1.618,
  file = get_mypath("figures", "matmet.png")
)
```

### 2021-08-25 paper/appendix.Rmd
Clean appendix

```{r, echo = FALSE, message = FALSE, collapse = FALSE}

library(drake)
library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
library(sf)
library(nlme)

@@

source(mypath("R/misc.R"))
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

@@

st_cap <- paste0(
  "Repartion of the", length(st_mono_trends_stable_rich_bm), " stations used in
  the data analysis.")

```

@@

```{r}
loadd(
  resume_bm_rich_mod_mono_trends,
  model_bm_rich_no_covar_no_inc_mono_trends,
  reg_table_bm_rich_mono_trends,
  reg_table_bm_rich_mono_stable_trends,
  reg_table_bm_rich_trends,
  reg_table_bm_rich,
  anova_table_bm_rich_mono_trends,
  anova_table_bm_rich_mono_stable_trends,
  anova_table_bm_rich_trends,
  anova_table_bm_rich,
  anova_bm_rich_mod
)
loadd(st_trends_rich_bm, st_mono_trends_rich_bm,
  st_mono_trends_stable_rich_bm)

loadd(pred_bm_rich_mono_trends, pred_bm_rich, pred_bm_rich_trends,
  pred_bm_rich_mono_stable_trends)
```

@@

### Only mono trends

We kept only the stations that had monotonic trends for biomass and species
richness, with resulting `r length(st_mono_trends_rich_bm)` stations.

```{r}

plot_grid(plotlist = pred_bm_rich_mono_trends$pred_plot)
```

```{r}
reg_table_bm_rich_mono_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of the network structure and the one of
      community biomass and species richness."
    ),
  label = "reg-rich-mono"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich_mono_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"ANOVA results for the links between the temporal trends of the network
	structure and the one of community biomass and species richness."
	),
      label = "aov-rich-mono"
      ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

### All trends (non monotonic)

We kept all stations that had a significant trend (decrease or increase) for both
species richness and community biomass, with resulting 
`r length(st_trends_rich_bm)` stations.

```{r}
plot_grid(plotlist = pred_bm_rich_trends$pred_plot)
```

```{r}
reg_table_bm_rich_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"Regression coefficients for the linear models explaining the links
	between the temporal trends of the network structure and the one of
	community biomass and species richness."
    ),
  label = "reg-rich-trends"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"ANOVA results for the links between the temporal trends of species
	richness and the temporal trends of the network structure."
	),
      label = "aov-rich-trends"
      ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

### All monotonic stations (i.e + monotonic stable)

```{r}
plot_grid(plotlist = pred_bm_rich_mono_stable_trends$pred_plot)
```

```{r}
reg_table_bm_rich_mono_stable_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"Regression coefficients for the linear models explaining the links
	between the temporal trends of the network structure and the one of
	community biomass and species richness."
    ),
  label = "reg-rich-trends"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich_mono_stable_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"ANOVA results for the links between the temporal trends of species
	richness and the temporal trends of the network structure."
	),
      label = "aov-rich-trends"
      ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

### All stations

We kept all the stations.

```{r}
plot_grid(plotlist = pred_bm_rich$pred_plot)
```

```{r}
reg_table_bm_rich %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"Regression coefficients for the linear models explaining the links
	between the temporal trends of the network structure and the one of
	community biomass and species richness."
    ),
  label = "reg-rich-all"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "ANOVA results for the links between the temporal trends of species
      richness and the temporal trends of the network structure."
      ),
    label = "aov-rich-all"
    ) %>%
kable_styling(latex_options =c("scale_down", "stripped")) %>%
collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
test <- pred_int_rich[3, ]$pred_int[[1]] %>%
  select(predicted, log_rich_std, log_bm_std) %>%
  arrange(log_rich_std, log_bm_std)

@@

```{r, eval=FALSE}
test <- model_bm_rich_int_mono_stable_trends[["ct_ff"]]
co <- coef(test)
pred <- ggpredict(
  test,
  terms = c("log_bm_std ", "log_rich_std")
  ) %>%
  as_tibble() %>%
  mutate(group = as.numeric(as.character(group))) %>%
  rename("log_bm_std" = x, "log_rich_std" = group)

@@

mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
library(plotly)
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "species richness"),
      yaxis = list(title = "Community biomass"),
      zaxis = list(title = "Connectance")
      ))
```

```{r, eval=FALSE}
mod4_3d <- model_bm_rich_int_mono_stable_trends[
  names(model_bm_rich_int_mono_stable_trends) %in%
    c("ct_ff", "w_trph_lvl_avg")]

```{r,eval=FALSE}
mat <- reshape2::acast(
  pred_list$w_trph_lvl_avg,
  log_rich_std~log_bm_std,
  value.var = "y")
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "Community biomass"),
      yaxis = list(title = "species richness"),
      zaxis = list(title = "Avg trophic level")
      ))
```

```{r,eval=FALSE}
test <- model_bm_rich_int_mono_stable_trends[["piel_bm"]]
car::Anova(test)
co <- coef(test)
pred <- ggpredict(
  test,
  terms = c("log_bm_std ", "log_rich_std")
  ) %>%
  as_tibble() %>%
  mutate(group = as.numeric(as.character(group))) %>%
  rename("log_bm_std" = x, "log_rich_std" = group)

mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "species richness"),
      yaxis = list(title = "Community biomass"),
      zaxis = list(title = "Eveness of biomass")
      ))
```

>>>>

```{r, echo = FALSE, message = FALSE, collapse = FALSE}
library(drake)
library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
library(sf)
library(nlme)

@@

source(mypath("R/misc.R"))
source_dir(mypath("R")) # Define your custom code as a bunch of functions.

@@

st_cap <- paste0(
  "Repartion of the", length(st_mono_trends_stable_rich_bm), " stations used in
  the data analysis.")
```

@@

```{r}
loadd(
  resume_bm_rich_mod_mono_trends,
  model_bm_rich_no_covar_no_inc_mono_trends,
  reg_table_bm_rich_mono_trends,
  reg_table_bm_rich_mono_stable_trends,
  reg_table_bm_rich_trends,
  reg_table_bm_rich,
  anova_table_bm_rich_mono_trends,
  anova_table_bm_rich_mono_stable_trends,
  anova_table_bm_rich_trends,
  anova_table_bm_rich,
  anova_bm_rich_mod
)
loadd(
  st_trends_rich_bm,
  st_mono_trends_rich_bm,
  st_mono_trends_stable_rich_bm,
  basin_station
)
loadd(
  pred_bm_rich_mono_trends,
  pred_bm_rich,
  pred_bm_rich_trends,
  pred_bm_rich_mono_stable_trends
)
```

@@

```{r sens, out.width="100%"}
# Merge reg_table
merged_reg_table <- pmap_dfr(
  list(
    df = list(
      reg_table_bm_rich_mono_trends,
      reg_table_bm_rich_mono_stable_trends,
      reg_table_bm_rich_trends,
      reg_table_bm_rich
      ),
    name = list(
      "Only monotonuous trends",
      "Monotonuous + stable trends",
      "All significant trends",
      "All trends"
      ),
    st = list(
      st_mono_trends_rich_bm,
      st_mono_trends_stable_rich_bm,
      st_trends_rich_bm,
      seq(1,400)
    )
    ), function (df, name, st) {
    df$selection <- paste0(name, " (N = ", length(st),")")
    return(select(df, selection, everything()))
  }
)

merged_reg_table %>%
  filter(! term %in% "(Intercept)", ! response %in% "piel_nind") %>%
  mutate(
   response = str_replace_all(response, var_replacement()),
   term = str_replace_all(term, var_replacement()),
  ) %>%
  ggplot(aes(x = term, y = std_estimate)) +
  geom_point(aes(color = selection)) +
  facet_grid(cols = vars(response)) +
  labs(
    x = "Explicative variable",
    y = "Standardized coefficients"
  ) +
  theme(legend.position = "bottom", axis.text.x = element_text(hjust=1, angle = 15))
```

@@

```{r eval = FALSE}
test <- pred_int_rich[3, ]$pred_int[[1]] %>%
  select(predicted, log_rich_std, log_bm_std) %>%
  arrange(log_rich_std, log_bm_std)

@@

```{r, echo=FALSE, eval=FALSE}
test <- model_bm_rich_int_mono_stable_trends[["ct_ff"]]
car::Anova(test)
co <- coef(test)
pred <- ggpredict(
  test,
  terms = c("log_bm_std ", "log_rich_std")
  ) %>%
  as_tibble() %>%
  mutate(group = as.numeric(as.character(group))) %>%
  rename("log_bm_std" = x, "log_rich_std" = group)

pred$y <- co[1] +
 # co["log_rich_std"] * pred[["log_rich_std"]] + bc not significant
  co["log_bm_std"] * pred[["log_bm_std"]] +
  co["log_rich_std:log_bm_std"] * pred[["log_rich_std"]] * pred[["log_bm_std"]]

mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
library(plotly)
p <- plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "species richness"),
      yaxis = list(title = "Community biomass"),
      zaxis = list(title = "Connectance")
      ))
```

```{r, result=FALSE}
mod4_3d <- model_bm_rich_int_mono_stable_trends[
  names(model_bm_rich_int_mono_stable_trends) %in%
    c("ct_ff", "w_trph_lvl_avg")]

```{r,result=FALSE}
mat <- reshape2::acast(
  pred_list$w_trph_lvl_avg,
  log_rich_std~log_bm_std,
  value.var = "y")
p <- plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "Community biomass"),
      yaxis = list(title = "species richness"),
      zaxis = list(title = "Avg trophic level")
      ))
```

```{r,result=FALSE, eval=FALSE}
test <- model_bm_rich_int_mono_stable_trends[["piel_bm"]]
car::Anova(test)
co <- coef(test)
pred <- ggpredict(
  test,
  terms = c("log_bm_std ", "log_rich_std")
  ) %>%
  as_tibble() %>%
  mutate(group = as.numeric(as.character(group))) %>%
  rename("log_bm_std" = x, "log_rich_std" = group)

@@

mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
p <- plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "species richness"),
      yaxis = list(title = "Community biomass"),
      zaxis = list(title = "Eveness of biomass")
      ))
```

```{r}
p_ct_ff <- ggdraw() +
    draw_image(get_mypath("figures", "int_rich_bm_cf_ff.png"), scale = 1)
p_tlvl <- ggdraw() +
    draw_image(get_mypath("figures", "int_rich_bm_tlvl.png"), scale = 1)
p_piel_bm <- ggdraw() +
    draw_image(get_mypath("figures", "int_rich_bm_eveness.png"), scale = 1)
plot_grid(
  p_ct_ff,
  p_tlvl,
  p_piel_bm
)
```

- Results for interactions: 
  - Connectance: 
    - Always decreases when richness decreases (inverse of expectation)
    - Increases when richness increases (inverse of expectation), but always
      decreases if biomass decreases
    - Increases when biomass increases
  - Average trophic level:
    - Always decreases when biomass decreases 
    - Always increases when biomass increases 
    - Whatever the richness dynamics, it is the biomass dynamics which drives
      all
  - Pielou of biomass:
    - Always positive when biomass decreases
    - Always negative when biomass increases

```{r}
template_cross <- tibble(
  bm_std = c("-", "0", "+"),
  `-` = c(NA, NA, NA),
  `0` = c(NA, NA, NA),
  `+` = c(NA, NA, NA),
  )

ct_ff_cross_table <- tibble(
  rich_std = c("-", "0", "+", "sign_relationship"),
  `-` = c("-", "-", "--", "-"),
  `0` = c("-", "-", "-", "0"),
  `+` = c("-", "+", "++", "+"),
  "sign_relationship" = c("0", "+", "+", "")
  )

kable(ct_ff_cross_table) %>%
  add_header_above(c(" " = 1, "bm_std" = 3))
```

```{r}
tlvl_cross_table <- tibble(
  rich_std = c("-", "0", "+", "sign_relationship"),
  `-` = c("-", "0", "+", "+"),
  `0` = c("-", "0", "+", "+"),
  `+` = c("-", "0", "+", "+"),
  "sign_relationship" = c("+", "0", "-", "")
  )

kable(tlvl_cross_table) %>%
  add_header_above(c(" " = 1, "bm_std" = 3))
```
